### 2020-06-01 notebook/import.Rmd
WIP :pen:

```{r zooplankton}
bench::bench_time(
  neon_download("DP1.20219.001",  quiet = TRUE)
)
```

```{r macroinvert}
bench::bench_time(neon_download("DP1.20120.001", quiet = TRUE))
```

```{r mozzies}
bench::bench_time(
  neon_download("DP1.10043.001", quiet = TRUE)
)
```

>>>>

```{r zooplankton}
neon_download("DP1.20219.001")
```

```{r macroinvert}
neon_download("DP1.20120.001")
```

```{r mozzies}
bench::bench_time(
  neon_download("DP1.10043.001")
)
```
